### 2025-04-21 sec/3_tls_opt.tex
Polish t solver

To minimize the WLS-relaxation over the translation $\mathbf{t}$ for obtaining the lower bound over the ball with center $\mathbf{c}$ and radius $n_r$, we need to solve the following optimization problem:
\begin{equation}
	\label{eq:tls-twls-constrained}
	\begin{aligned}
		\argmin_{\mathbf{x} \in \Rone^3} \quad &\sum_{i=1}^{N} w_i ||\mathbf{d}_i - \mathbf{x}||_2^2 \\
		\text{subject to} \quad  &||\mathbf{x}||_2 \leq n_r
	\end{aligned}
\end{equation}

where 
\begin{equation}
	\begin{aligned}
		\mathbf{x} = \mathbf{c} - \mathbf{t}  \iff  \mathbf{t} = \mathbf{c} - \mathbf{x}\\
		\mathbf{d}_i = \mathbf{a}_i - \mathbf{b}_i + \mathbf{c}
	\end{aligned}
\end{equation}

The constraint $||\mathbf{x}||_2 \leq n_r$ ensures that the found $\mathbf{x}$ is inside the BnB node. The other sums of the convex relaxation \ref{eq:tls-wls-relaxation1} disappeared because they are constant (i.e. they do not depend on $\mathbf{x}$). This problem is a convex QCQP and therefore solvable by any standard QCQP solver. However, we show that the solution can be obtained even more easily in closed form, which in practice results in a much faster algorithm.

We first form the Lagrangian to account for the constraint (which is squared):

\begin{equation}
	\begin{aligned}	
		L(\mathbf{x}, \lambda) =  \sum_{i=1}^{N} w_i ||\mathbf{d}_i - \mathbf{x}||_2^2 + \lambda (
		\mathbf{x}^\transposed \mathbf{x} - n_r^2)\\
	\end{aligned}
\end{equation}

>>>>

The problem of minimizing the WLS-relaxation over a ball $\{ \mathbf{t} : || \mathbf{c} - \mathbf{t} || \leq n_r \}$ of translations is:
\begin{equation}
	\label{eq:tls-twls-constrained}
	\begin{aligned}
		\argmin_{\mathbf{x} \in \Rone^3} \quad &\sum_{i=1}^{N} w_i ||\mathbf{a}_i - \mathbf{b}_i + \mathbf{c} - \mathbf{t}||_2^2 \\
		\text{subject to} \quad  &||\mathbf{c} - \mathbf{t}||_2 \leq n_r
	\end{aligned}
\end{equation}

The ball center $\mathbf{c}$ is the center of the BnB node that has a radius $n_r$. 
The constraint $||\mathbf{c} - \mathbf{t}||_2 \leq n_r$ therefore ensures  that the found $\mathbf{t}$ is inside the BnB node. Note that compared to the definition of the convex relaxation \ref{eq:tls-wls-relaxation1}, two constant sums disappeared because they are constant (i.e. they do not depend on $\mathbf{t}$). 
We can write this problem equivalently as:
\begin{equation}
	\label{eq:tls-twls-constrained}
	\begin{aligned}
		\argmin_{\mathbf{x} \in \Rone^3} \quad &\sum_{i=1}^{N} w_i ||\mathbf{d}_i - \mathbf{x}||_2^2 \\
		\text{subject to} \quad  &||\mathbf{x}||_2 \leq n_r
	\end{aligned}
\end{equation}
with 
\begin{equation}
	\begin{aligned}
		\mathbf{x} = \mathbf{c} - \mathbf{t}, \quad \mathbf{d}_i = \mathbf{a}_i - \mathbf{b}_i + \mathbf{c}
	\end{aligned}
\end{equation}

This problem can be solved easily in closed form.
We first form the Lagrangian to account for the constraint:
\begin{equation}
	\begin{aligned}	
		L(\mathbf{x}, \lambda) =  \sum_{i=1}^{N} w_i ||\mathbf{d}_i - \mathbf{x}||_2^2 + \lambda (
		\mathbf{x}^\transposed \mathbf{x} - n_r^2)\\
	\end{aligned}
\end{equation}
